A High Efficiency MAC Protocol for WLANs: Providing Fairness in Dense Scenarios

### 2015-10-07 results.tex
Changed all the figures to comply with the new style and order

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/saturated/timeBetweenSxTx-sat/timeBetweenSxTx-multiplot-sat.eps}
		\caption{Average time between successful transmissions: averaging over all stations}
		\label{fig:serviceTime-sat}
	\end{figure}

@@

   	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/throughput-unsaturated/throughput-unsaturated-w-BOS.eps}
		\caption{Throughput in non-saturation conditions}
		\label{fig:throughputUnsat}
	\end{figure}

@@

   	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/collision-unsaturated/collisions-unsaturated.eps}
		\caption{Average percentage of collision slots: the fraction of time slots containing collisions in non-saturated conditions}
		\label{fig:collisions-unsat}
	\end{figure}

   	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/droppedPackets/droppedPacketsDueRET.eps}
		\caption{Percentage of droppped packets due to reaching the retransmission threshold}
		\label{fig:droppedDueToRET}
	\end{figure}

	 \begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/queueSize/queueSize-multiplot.eps}
		\caption{Average number of packets in the MAC queue of a node}
		\label{fig:MacQ}
	\end{figure}

@@

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/queueingDelay/queueingDelay-multiplot.eps}
		\caption{Average system delay: averaging over all stations}
		\label{fig:serviceTime-unsat}
	\end{figure}

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/blockingProb-unsat/blocking-unsaturated.eps}
		\caption{Average fraction of blocked packets. When the MAC queue is full, packets comming from the uppers layers must be discarded or blocked}
		\label{fig:blocked-packets}
	\end{figure}

@@

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/timeBetweenSxTx-unsat/timeBetweenSxTx-multiplot-unsat2.eps}
		\caption{Average time between successful transmissions in non-saturated conditions: averaging over all stations}
		\label{fig:timeBetweenSxTx-multiplot-unsat}
	\end{figure}

@@

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/saturated/mixed/throughput-mixed/throughput-saturated-mixed.eps}
		\caption{Network throughput when composed by various proportions of CSMA/CA and CSMA/ECA$_{\text{Hys+FS}}$ nodes}
		\label{fig:mixedThroughput-sat}
	\end{figure}

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/saturated/mixed/collisions-mixed/collisions-mixed-saturated.eps}
		\caption{Average percentage of collision slots for the tested mixed network setups proportions}
		\label{fig:mixedCollisions-sat}
	\end{figure}

	\begin{figure}[tb!!!]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/mixed/throughput-mixed/throughput-unsaturated-mixed.eps}
		\caption{Network throughput when composed by various proportions of non-saturated CSMA/CA and CSMA/ECA$_{\text{Hys+FS}}$ nodes}
		\label{fig:mixedThroughput-unsat}
	\end{figure}

	\begin{figure}[tb!!!]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/mixed/collisions-mixed/collisions-mixed-unsaturated.eps}
		\caption{Average percentage of collision slots for the tested mixed network setups proportions in non-saturated conditions}
		\label{fig:mixCollisions-unsat}
	\end{figure}

>>>>

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/saturated/timeBetweenSxTx-sat/timeBetweenSxTx-multiplot-sat-TON.eps}
		\caption{Average time between successful transmissions: averaging over all stations}
		\label{fig:serviceTime-sat}
	\end{figure}

@@

   	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/throughput-unsaturated/throughput-unsaturated-w-BOS-TON.eps}
		\caption{Throughput in non-saturation conditions}
		\label{fig:throughputUnsat}
	\end{figure}

@@

   	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/collision-unsaturated/collisions-unsaturated-TON.eps}
		\caption{Average percentage of collision slots: the fraction of time slots containing collisions in non-saturated conditions}
		\label{fig:collisions-unsat}
	\end{figure}

   	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/droppedPackets/droppedPacketsDueRET-TON.eps}
		\caption{Percentage of droppped packets due to reaching the retransmission threshold}
		\label{fig:droppedDueToRET}
	\end{figure}

	 \begin{figure}[tb]
		\centering				
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/queueSize/queueSize-multiplot-TON.eps}
		\caption{Average number of packets in the MAC queue of a node}
		\label{fig:MacQ}
	\end{figure}

@@

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/queueingDelay/queueingDelay-TON.eps}
		\caption{Average system delay: averaging over all stations}
		\label{fig:serviceTime-unsat}
	\end{figure}

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/blockingProb-unsat/blocking-unsaturated-TON.eps}
		\caption{Average fraction of blocked packets. When the MAC queue is full, packets comming from the uppers layers must be discarded or blocked}
		\label{fig:blocked-packets}
	\end{figure}

@@

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/timeBetweenSxTx-unsat/timeBetweenSxTx-multiplot-unsat-TON.eps}
		\caption{Average time between successful transmissions in non-saturated conditions: averaging over all stations}
		\label{fig:timeBetweenSxTx-multiplot-unsat}
	\end{figure}

@@

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/saturated/mixed/throughput-mixed/throughput-saturated-mixed-TON.eps}
		\caption{Network throughput when composed by various proportions of CSMA/CA and CSMA/ECA$_{\text{Hys+FS}}$ nodes}
		\label{fig:mixedThroughput-sat}
	\end{figure}

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/saturated/mixed/collisions-mixed/collisions-mixed-saturated-TON.eps}
		\caption{Average percentage of collision slots for the tested mixed network setups proportions}
		\label{fig:mixedCollisions-sat}
	\end{figure}

	\begin{figure}[tb!!!]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/mixed/throughput-mixed/throughput-unsaturated-mixed-TON.eps}
		\caption{Network throughput when composed by various proportions of non-saturated CSMA/CA and CSMA/ECA$_{\text{Hys+FS}}$ nodes}
		\label{fig:mixedThroughput-unsat}
	\end{figure}

	\begin{figure}[tb!!!]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/mixed/collisions-mixed/collisions-mixed-unsaturated-TON.eps}
		\caption{Average percentage of collision slots for the tested mixed network setups proportions in non-saturated conditions}
		\label{fig:mixCollisions-unsat}
	\end{figure}
